---
title: "Untitled"
author: "Jonathan Bourne"
date: "24/07/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

r.peach13@imperial.ac.uk 

https://journals.aps.org/prresearch/abstract/10.1103/PhysRevResearch.1.033211 

A network science approach towards studying protein folding

Measuring and mitigating behavioural segregation using Call Data Records -P
Community detection with node attributes in multilayer networks ( -p

poster sesson 7
Stochastic dimensional reduction on large biological neural networks -p
Enhancing transport properties in interconnected systems without altering their structure  -p
Revealing Organizational Structures by Studying Activity Patterns in Social Networks -p

poster session 10
Brain communication is shaped by cortical hierarchies -p

The goal of this code is to test whether SETSe can integrate both the strength of relationships between people, the greater social network and the individual belligerents to predict the outcome of a conflict, or alternatively ascertain the strength of different relationship types from known outcomes.

#concept

The importance of relationship strength in mediating partisanship during social conflict in a social network

This paper demonstrates the importance of position in topology of the two beligerents, the strategic importance of certain topologies when it comes to success in conflict.

I also demonstrate how the inverse is true, and that unknown relationship strengths can be determined given a conflict outcome.

This paper explores how the strenght of a connection between individuals affects which side of a conflict individuals take

#Set up
```{r Setup}

packages <- c("tidyverse", "igraph","readr","readxl", "broom", "stringr", "xtable", "rlang", "latex2exp", "yardstick", "ggraph", "patchwork", "rsample", "VGAM", "class", "mclust", "R.matlab", "ranger")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

select <- dplyr::select
arrange <- dplyr::arrange
map <- purrr::map
sapply(packages, library, character.only = TRUE)

library(rsetse)
library(ConflictInternal)
#Set up file system to read the correct folders this switches between aws and windows mode

#set this to your root
basewd <- "/home/jonno"

conflict_folder <- file.path(basewd, "SETSe_conflict")

#all the other folders can go from there
LatexFolder <- file.path(basewd,"Dropbox/Apps/ShareLaTeX/Sets Paper 3" )
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
PLwd <- file.path(basewd,"/setse_1_data")
CodeFolder <- file.path(basewd,"SETSe_assortativity_and_clusters")
SubcodeFolder <- file.path(CodeFolder, "sub_code")


#block this off to see what is being used from there
# #Load some other useful functions
# list.files("/home/jonno/Useful_PhD__R_Functions", pattern = ".R", full.names = T) %>%
#   walk(~source(.x))


```

#Plot peels
```{r}
set.seed(123)
quintet_g_list<- LETTERS[1:5] %>% map(~{
      nodes <- 0
      while(nodes !=40){
        g <- generate_peels_network(type = .x ) %>%
          remove_small_components()
        nodes <- vcount(g)
      }
return(g)
})

set.seed(123)
plot_list <- 1:5 %>%
  map(~{
    out <- ggraph(quintet_g_list[[.x]]) +
      geom_edge_fan()+
      geom_node_point(aes(colour = sub_class), size=3) +
      labs(title = paste("Type", LETTERS[.x]))
    
    if(.x !=5){
       print(.x)
      out <- out + guides(colour = "none") 
    }
    
    return(out)
    
    })


 (plot_list[[1]] | plot_list[[2]] | plot_list[[3]] )/
     (plot_list[[4]]| plot_list[[5]]) +
   plot_annotation(
  title = "The Peels quintet of assortativty identical graphs, coloured by subgraph-type",
#  subtitle = 'The graphs can be separated using SETSe'
)
ggsave(file.path(FiguresFolder,  "peel_quintet.pdf"))       

```

 
#simple case

This is a few toy examples to show that nodes with stiffer springs will have neighbouring nodes closer than nodes with less stuff springs. The purpose of these examples is to act as explainer and motivator for the idea that SETSe can predict conflict outcome or edge strenth

```{r}

```



#example conflicts
This section generates a number of networks using some method. It applies edge strengths and shows that consistant edge rules provide consistant results across randomly generated networks and node positions.

all experiments should comment on the comparison with betweeness centrality and also community detection techniques. This should show that SETSe can produce an outcome that the other methods can't

##Fixed edge strengths
This section uses fixed edge strengths for each relationship type.

generate network

If I generate 100 examples of each combination of agreement for all graph types, then plot the win ratio matrices for all combinations. This will show that certain subclasses have an advantage over others and this differs according to network topology.

I can then change the edge weights and repeat. this will show the importance of edge weights in the result.

#fixed/variable outcome comparison
Data is loaded from HPC script
```{r}

peel_files <- list.files("/home/jonno/conflict_data/peelconflict", full.names = T, pattern = ".rds")


#How many of each type? did they all complete?
paired_results <- LETTERS[1:5] %>% map_df(~{
  total_graph_type <- peel_files[which(grepl(pattern = paste0(.x, "_seed"), x = peel_files))]
  
  completed_graphs <- basename(total_graph_type) %>% str_remove(., ".rds") %>% str_remove(., "peel_conflict_k_") %>%
    tibble(clean_name = .) %>%
    separate(., clean_name, into = c("type", "drop", "drop2", "drop3", "seed")) %>%
    select(-contains("drop")) 
  
  out <- full_join(completed_graphs %>%
                                filter(type == "uniform") %>%
                                select(seed
                                ) %>% mutate(uniform = TRUE)
                              ,
                              completed_graphs %>%
                                filter(type == "varies") %>%
                                select( seed
                                ) %>% mutate(varies = TRUE),
                              by = "seed") %>%
    mutate(
      seed = as.integer(seed),
      is_pair = complete.cases(.),
      graph_type = .x)  %>%
    arrange(seed)
  
  return(out)
  
  
})


#This finds out how the ranking of individual nodes changes when they have uniform or variable edge strengths on the same network.
node_performance <-  LETTERS[1:5] %>% map_df(~{
  peel_files <- peel_files[which(grepl(pattern = .x, x = peel_files))]

  paired_results_TRUE <- paired_results %>%
  filter(#is_pair ==T,
         graph_type==.x)
  
  graph_type <- .x
  
  #only compares paired networks. this is in the case that some networks don't converge fast enough
  paired_results_TRUE$seed %>% map_df(~{
    peel_files2 <- peel_files[which(grepl(pattern = paste0("seed_", .x, ".rds"), x = peel_files))]
    
  peel_conflict_performance(read_rds(peel_files2[2]), read_rds(peel_files2[1])) %>%
    mutate(graph_type = graph_type)
    
  })
    })


#Networks with kess clear structure have larger changes in node performance when edge strength is changed
node_performance  %>%
  mutate(
    win_fract = wins/(wins+loss),
    win_fract_uniform = wins_uniform/(wins_uniform+loss_uniform),
    win_fract_relative = win_fract -win_fract_uniform,
    relative_wins = (wins/loss)/(wins_uniform/loss_uniform)) %>%
  ggplot(aes(x = win_fract, y = win_fract_uniform)) + geom_hex()+
  facet_wrap(~graph_type)


#second version that should be simpler
peels_results <- read_rds(peel_files[1])
sub_class_performance <-  peel_files %>% map_df(~{
  #print every 100 to show progress
  if(( grep(.x, peel_files)) %%100 == 0) {print(grep(.x, peel_files))}
  file_name <- .x %>%
    str_remove(., ".rds") %>%
    str_split(, pattern = "_", simplify = TRUE)
  
  temp <- read_rds(.x)  %>%
    bind_rows(read_rds(.x) %>%
                rename(sub_class3 = sub_class, 
                       sub_class = sub_class2,
                       node3 = node1,
                       node1 = node2) %>%
                rename(sub_class2 = sub_class3,
                       node2 = node3) %>%
                mutate(across(contains("fract"), ~1-.x),
                       betweenness_ratio = 1/betweenness_ratio)) %>%
    group_by(sub_class, sub_class2, graph_type, sample) %>%
    summarise(wins = sum(clustering_elev_fract>0.5),
              draws = sum(clustering_elev_fract==0.5),
              loss = sum(clustering_elev_fract<0.5), .groups = "drop")%>%
    mutate(k_type = file_name[[5]],
           seed = as.integer(file_name[9]))
  
}) %>%
  mutate(
    name =  paste(sub_class, sub_class2) %>% str_remove_all(., "_"),
    win_fract = wins/(wins+loss),
    k_type = str_remove(k_type, "n")) %>%
  separate(col = k_type, sep = "[a-z]", into = c("near", "medium", "far"), convert = T, remove = F)

#the above code chunk removes the need for the function
#    peel_conflict_subclass_performance

sub_class_performance  %>%
  filter(k_type == "1000m550f100" | k_type == "100m550f1000") %>%
  select(-c(wins, draws, loss, near, medium, far)) %>%
  pivot_wider(names_from = k_type, values_from = win_fract) %>%
  ggplot(aes(x = `1000m550f100`, y = `100m550f1000`)) + geom_hex()+
  facet_wrap(~graph_type)

sub_graph_pairs <- sub_class_performance %>%
  group_by(sub_class, sub_class2, graph_type, k_type) %>%
  summarise_all(mean) %>%
  mutate(beligerents = paste(sub_class, sub_class2) %>% str_remove_all(., "_"))


#Clear strategic advantages are visible between network regions
sub_graph_pairs %>%
  filter(k_type == "n1000m550f100" ) %>%
  ggplot(aes(x = sub_class, y = sub_class2, fill =  win_fract  )) + 
  geom_raster() +
  facet_wrap(~graph_type) +
  scale_fill_viridis(option = "C")


#keeps only one side of the competition. Usefull for keeping the figures simple and not repeating information
keep_ids <- combn(unique(sub_graph_pairs$sub_class),2) %>% t %>% as_tibble %>%
  setNames(., c("sub_class", "sub_class2")) %>%
  mutate(names = paste(sub_class, sub_class2) %>% str_remove_all(., "_"))

sub_graph_pairs %>%
  filter(graph_type!="A",
         k_type =="n1000m550f100") %>%
    filter(beligerents %in% keep_ids$names) %>%
  ggplot(aes(x = draws/100, y = win_fract, colour = beligerents)) + 
   facet_wrap(~graph_type) +
    geom_point() +
  coord_cartesian(xlim = c(0,0.6))

sub_class_performance <- sub_class_performance %>%
  mutate(k_type = str_remove(k_type, "n")) %>%
  separate(col = k_type, sep = "[a-z]", into = c("near", "medium", "far"), convert = T, remove = F) %>%
  mutate(ratio = near/far,
         ratio_chr = factor(paste(near/100, far/100, sep = "/")),
         ratio_chr = fct_reorder(ratio_chr, ratio))



#This plot shows that there are dominant strategic positions in the network defined by connection type.
#These positions are strongly corellated with centrality
#Varying the edge connection strength can cause significant change in outcome although in these networks the dominance of the sub-class is not reversed.
#However within specific networks, the changes within individual networks can have a change in win ratio between the sections of almost 50% percentage points completely reversing the win ratio between two sub_classes
#For some networks non-uniform edges can produce more stable/unstable results although the mean is unchanged.

#One qeustion is which combinations deviate most from the centrality dominance position and why?
#Also what is the ability of tradtional clustering to make the same separation?
sub_class_performance %>%
    filter(graph_type!="A",
           near == 1000|medium==100|far ==1000) %>%
  #mutate(k_type = factor(k_type, levels = c("low", "uniform", "high"))) %>%
# filter(graph_type !="E") %>%
  filter(name %in% keep_ids$names) %>%
 # select(name, win_fract, graph_type) %>%
 # pivot_longer(cols = c(win_fract), names_to = "type") %>%
  #mutate(type = ifelse(type =="win_fract", "varies", "uniform")) %>%
  ggplot(aes(x = name,
             y = win_fract, #draw_diff, 
             fill =k_type)) + geom_boxplot() +
  facet_wrap(~graph_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Win probability for each sub-graph pair on networks",
       x = "The sub-classes of the two beligerents",
       y = "Win fraction of the first beligerent")
ggsave(file.path(FiguresFolder, "wins_to_losses.pdf"))



sub_class_performance %>%
  group_by(ratio_chr, ratio, graph_type, name ) %>%
  summarise(win_fract = mean(win_fract)) %>%
    filter(#graph_type!="A",
           name %in% keep_ids$names) %>%
  ggplot(aes(colour = name,
             y = win_fract, #draw_diff, 
             x =ratio_chr,
             group = name)) + geom_line() +
  facet_wrap(~graph_type)

```

##Centrality

This block compares the relative centrality of the nodes to the probability of winning. Being more central is an advantage but does not generally determine the winner. 

This is becuase the supporting network is also important.

```{r}

node_performance <- LETTERS[1:5] %>% map_df(~{
  peel_files <- peel_files[which(grepl(pattern = .x, x = peel_files))]
  
  graph_type <- .x
  
  1:length(peel_files) %>% map_df(~{
    
    temp <- read_rds(peel_files[.x])
    
    test <- temp %>%
  mutate(win = temp$clustering_elev_fract>0.5,
         loss = temp$clustering_elev_fract<0.5,
         draw = temp$clustering_elev_fract==0.5,
         status = case_when(
           win ~"win",
           loss~"loss",
           TRUE ~"draw"
         ),
         betweeness_greater = betweenness_ratio>1,
         betweeness_greater = ifelse(is.na(betweeness_greater), "even", 
                                     tolower(as.character(betweeness_greater))),
         betweeness_win = case_when(
           betweeness_greater=="true" ~"win",
           betweeness_greater == "false" ~"loss",
           TRUE ~ "draw"
         ),
         winner_greater_betweenness = case_when(
           status == "loss" & betweeness_greater=="false" ~TRUE,
           status == "win" & betweeness_greater == "true" ~TRUE,
           TRUE ~FALSE
         ),
         file = basename(peel_files[.x]))
    
return(test)

    
  })
    }) %>% 
  separate(., col = file, into = c(paste0("drop", 1:3), "k_type", "drop4", "graph_type", "drop5", "seed"), sep = "_") %>%
  mutate(seed = str_remove(seed, ".rds") %>% as.integer()) %>%
  select(-contains("drop"))

#generally wins when betweenness greater. but this is not a huge margin.
#about 60% or something
table(node_performance$status, node_performance$betweeness_greater)
#This finding is consistant across the graph types
table(node_performance$winner_greater_betweenness, node_performance$graph_type)


#Betweeness and SETSe only agree 58% of the time,or 64% if A is excluded . This is because SETSe using information provided from across the network not just the direct paths.
#There is very little change in performance of betweeness between the variable an fixed edge strengths

unique(node_performance$k_type) %>%
  map_df(~{
    node_performance %>%
           filter(k_type ==.x) %>%
    accuracy(., estimate = as.factor(betweeness_win), truth = as.factor(status)) %>%
      mutate(type = .x)
    
  })

unique(node_performance$k_type) %>%
  map_df(~{
    node_performance %>%
           filter(k_type ==.x,
                  graph_type != "A") %>%
    accuracy(., estimate = as.factor(betweeness_win), truth = as.factor(status)) %>%
      mutate(type = .x)
    
  })



# sub_class_graph_combos <- expand_grid(k_type = unique(node_performance$k_type), 
#             paired_results %>% #filter(is_pair) %>% 
#               select(seed, graph_type),
#             distinct(node_performance %>% select(sub_class, sub_class2))) %>%
#   mutate(id = 1:n())
#takes a long time. save results and load again
sub_class_graph_combos <- expand_grid(k_type = unique(node_performance$k_type), 
            seed = 1:100,
            graph_type = LETTERS[1:5],
            distinct(node_performance %>% select(sub_class, sub_class2))) %>%
  mutate(id = 1:n())

sub_class_betweeness_accuracy <- 1:nrow(sub_class_graph_combos) %>%
  map_df(~{ 
    
    temp <-sub_class_graph_combos %>%
      slice(.x)
    
    node_performance %>%
      filter(k_type ==temp$k_type,
             graph_type == temp$graph_type,
             sub_class == temp$sub_class,
             sub_class2 == temp$sub_class2,
             seed == temp$seed) %>%
      accuracy(., estimate = factor(betweeness_win, levels = c("draw", "loss", "win")), 
               truth = factor(status, levels = c("draw", "loss", "win"))) %>%
      mutate(id = .x,
             k_type =temp$k_type,
             graph_type = temp$graph_type,
             sub_class = temp$sub_class,
             sub_class2 = temp$sub_class2,
             seed = temp$seed)
    })  %>%
 mutate(name =  paste(sub_class, sub_class2) %>% str_remove_all(., "_")) %>%
    filter(name %in% keep_ids$names)

#This bar chart shows that certain topologies are much less easy to predict using betweeness than others
#Graph type A is very hard as it is an ER graph the 
#In addition when the edge strength varies there can be substantial changes in the predictive power of the betweeness.
#This shows that depending on the network topology and the weighting of the edges the betweeness cannot be thought of as a reliable predictor of win outcome

#This is the mean relative performance averaged across each network
sub_class_betweeness_accuracy %>%
    mutate(k_type = factor(k_type, levels = c("low", "uniform","high"))) %>%
  filter(graph_type!="A") %>%
    filter(name %in% keep_ids$names) %>%
  ggplot(aes(x = name, y= .estimate, fill = k_type)) + 
  facet_wrap(~graph_type) +
  geom_boxplot(position = "dodge") +
  labs(title = "Betweeness as a predictor of winning the competition",
       x = "The sub-classes of the two beligerents",
       y = "probability of highest betweeness node winning competition",
       fill = "k type")


#Separating the beligerents into separate clusters was not particularly successful. This is not a surprise given that there is no topological basis for the separation. SETSe seperated the beligerents 100% of the time which is what should happen.
#Given how poorly they separate the beligerents it is irrelevant who they predict the winner to be.
node_performance %>%
  select(contains("success")) %>%
  summarise_all(mean)


tibble(r =  seq(-1000,1000, 200 ),
       k_far = ifelse(r<0, abs(r), 100),
       k_mid = ifelse(r==0, 100, (abs(r)-100)/2 +100),
       k_near = ifelse(r>0, abs(r), 100))






#This chunk extracts the time taken by the HPC for each job
#As the time can be in mm:ss or hh:mm:ss format slight changes are made to ensure
#that they can all be correctly converted to time units
time_taken_df <- list.files("/home/jonno/conflict_data/peelconflict", 
                        pattern = "peelconflict.e4825498", full.names = T) %>%
  map_df(~{
  
 print_data <- read_lines(.x)

tibble( time = print_data[grep("Elapsed ", print_data)] %>% str_remove_all("\\\tElapsed \\(wall clock\\) time \\(h:mm:ss or m:ss\\): "), 
       file_id = basename(.x) %>% str_remove(., "peelconflict.e4825498.") %>% as.numeric())

})  %>%
  mutate(time_length = str_count(time, pattern = ":"),
         time2 = ifelse(time_length==1, paste0("00:", time), time),
         time2 = hms(time2))

#mean time is 30 mins. not too bad at all
mean(time_taken_df$time2)

flux=c(-2,-4,1,-2,4,11)
sign(flux)
diff(sign(flux))

updn <- c(0, diff(sign(flux)))
ix <- which(updn != 0)

```



comparing the conflict of everynode to every other node allows us to find nodes that are better positioned for that network setup. either purely topologically or accounting for edge strength

comparing the same graph using different edge strength allows a direct comparison of the impact of edge strength.

We can then identify the nodes who experience the greatest relative strength change when accounting for edges and the point at which the switch occurs


randomly assign edge strengths
```{r}

```


##Distribution edges

This shows the effect of using increaingly wide ranges of possible edge stiffnesses to predict the outcome of conflict.
I expect that when the uncertainty becomes larger the reliability drops.




#Conflict networks

This section looks at networks that experienced conflict and how the alliagieance of the network splits
all the data is from http://vlado.fmf.uni-lj.si/pub/networks/data/ucinet/UciData.htm#sampson
```{r}
files <- list.files("/home/jonno/setse_1_data/conflict_networks", full.names = T)
```


This is the thesis associated with a collection of schools dataset.
I don't know if there is any school level information available

https://search-proquest-com.libproxy.ucl.ac.uk/docview/304516167?pq-origsite=primo

data set available from; there are some problems with it.
http://moreno.ss.uci.edu/data.html

##Medici

The traditional metrics can check what would happen if we vary the strength of the different relationships
But only SETSe can vary the beligerents

This chunk shows that although the Strozzi have more power than the Albizzi, they would have lost in a congflict against the Medici, the Albizzi who although were split against and for the medici could have overpowered them if the strength of a mariage connection was no more than twice as valuable than a business connection. After that point the Albizzi lose badly.

The traditional metrics are identical for both of the conlfict types and in fact walktrap fails to separate the beligerents for large weights of marraige ties.

```{r}

#What is notable is that the medici can lose the conflict but are never less central  (lowwr betweeness) than the Strozzi or the Albizzi. This supports the simple case of a line of nodes where the centrality  of the nodes at each end is equal.

medici_df <- medici_process(files[5], files[6])

medici_df$AlbizziandStrozzi %>%
  filter(separate_success) %>%
  select(1:6, ratio) %>%
  pivot_longer(cols = 2:6, names_to = "metric", values_to = "values") %>%
    filter(metric !="ARI") %>%
  mutate(name = str_replace(name, "Elev", "Medici") %>% as.factor()  %>% str_remove(., "clustering_") %>% str_replace(., "_", " "),
         name = fct_relevel(name, "fast greedy", after = 2)) %>%
  ggplot(aes(x = ratio, y = values, colour = name, group = name)) + geom_path() +
  facet_wrap(~metric) +
  labs(title = "Medici vs Oligarchs using different power metrics",
       x = "Odds ratio of business to marriage weights",
       y = "Medici factional control",
       colour = "method") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
ggsave(file.path(FiguresFolder,  "medici_factional_controll.pdf"))       


set.seed(345)
medici_df$g_medici %>%
  delete_vertices(., vertex_attr(., "name")=="PUCCI" ) %>%
  ggraph(.) + 
    geom_edge_link2( width = 0.7, edge_alpha =0.5) + 
      geom_node_point( aes(colour = party, 
                           size = ifelse(name == "MEDICI"| name =="STROZZI", 6,3))) + 
    scale_size_continuous(range = c(3, 6))+
  scale_edge_colour_viridis() +
  labs(title = "The factional alligiance of the Florentine families network") +
  guides( size = "none")+
geom_node_text(aes(label = name), nudge_y = .08)
ggsave(file.path(FiguresFolder,  "Medici_partisan_network.pdf"))



betweenness(medici_df$g_medici, normalized = T)
#the elevation and groups plot
# medici_strozzi$groups %>%
#   filter(marriage_weight == 300, business_weight == 100) %>%
#   ggplot(aes(x = node, y = elevation, colour = factor(party),
#              size = ifelse(node == "MEDICI"| node =="STROZZI", 6,3))) + geom_point() +
#   scale_size_continuous(range = c(3, 6))+
#   guides( size = "none") + 
#   theme(axis.text.x = element_text(angle = 25, hjust = 1))+
#   labs(title = "Medici vs Strozzi a tug of war with the families of Florence",
#        x = "Family",
#        colour = "Faction")

```

##Kapferer Mine

multiplex ties can be considered strong ties and uniplex considered weak ties.

Jackson is the boss
Lotson is the shop steward

Donald and Able worked as a pair
Abraham and Benson worked as a pair


What we learn from this dataset is that the imoprtance of the difference in weighting becomes explicit in SETSe whilst it is implicit in the the traditional clustering metrics. As such the weighting can be learned through multiple observations of interactions within graph structures, this weighting can then be deployed on new observations. This is beyond the scope of this paper!

Using a weighting of from 1to1 to 100to1 we find that the meta weight edges is an important concept to consider. Abraham does not overpower Donald in the full netowrk until multi edges are worth 5 times more than uniplex edges. This is important as edges of a multiplex network are often considered equally weighted but this may not be the case, as an example regular work contact is not necessarily as valuable in conflict as regular friendly contact.

Irrespective of the relation between uni and multi edges Benson could never overcome Abel. What's more it required a higher weighting to for Abraham to overcome Abel, it thus appears the strategically most sensible move for Abraham to accuse Donald.

This information is not possible in a normal community detection algorithm which would always break the network into identical communities. The edge weights can be changed but this assumption has to be explicity stated using SETSe wheras the assumption is implicit in the other algorithms.

```{r}

test <- create_kapferer(files)

source(file = file.path(SubcodeFolder, "kapferer_process.R"))
#SETSE separates the beliggerants everytime as expected, however the other methods can only achieve this on certain parameter settings. That said they do sucessfully show that the Abraham would have beet Donald. They are much less 
Kapferer_aggregated %>%
  left_join(kapferer_separation) %>%
  filter(value == "Abraham"| value == "Benson", 
        # cluster_method == "SETSe_kmeans",
        separate_success,
        cluster_method != "SETSe_kmeans"
         ) %>%
  ggplot(aes(x = ratio, y = fract, colour =str_remove(cluster_method, "clustering_") %>% str_replace(., "_", " "))) + geom_line() +
  coord_cartesian(ylim = c(0,1)) +
  facet_wrap( ~combo)+
  labs(title = "Resolution of the Kapferer mine conflict on graphs of different weights",
       y = "fraction of workers who side with Abraham/Benson",
       x = "The value of multiple edges compared to a single edge",
       colour = "method")
ggsave(file.path(FiguresFolder,  "Kapferer_mine_results.pdf"))

test <-Kapferer_aggregated %>%
  group_by(combo, 
           ratio,
           cluster_method) %>%
  summarise(separation_failure = sum(is.na(value)))


spec_res <- Kapferer_embeddings_results %>%
  filter(combo  == "Abraham-Abel",
         ratio ==10)

spec_res %>%
  ggplot(aes(x = node, y = elevation, colour = SETSe_kmeans,
              size = ifelse(node == "MEDICI"| node =="STROZZI", 6,3))) + geom_point() +
  scale_size_continuous(range = c(3, 6))+
  guides( size = "none") + 
  theme(axis.text.x = element_text(angle = 25, hjust = 1))

as_data_frame(kapferer_mine_g) %>%
  graph_from_data_frame(., directed = FALSE, vertices = spec_res ) %>%
    ggraph(.) + 
    geom_edge_link2( width = 0.7, edge_alpha =0.5) + 
    geom_node_point( aes(
      colour = SETSe_kmeans,
      size = ifelse(name == "Abraham"| name =="Donald", 6,3))
    )  +   
  scale_size_continuous(range = c(3, 6))+
    scale_edge_colour_viridis() +
    labs(title = "Kapferer mine conflict") +
    guides( size = "none")+
    geom_node_text(aes(label = name), nudge_y = .08)
  


```

##Thurman Office

A whole host of crazy happened here this is to test what I can do with it

The Thurman office conflict "In the office: Networks and coalitions"
https://doi.org/10.1016/0378-8733(79)90010-8


Ann beats Emma

Conflict 1
factions Ann vs Emma : Ann Wins

For Ann
Tina
Jamie
Drew
Several Secretaries and Managers

Conflict x not really a conflict?
Emma vs Group

Emma
Rose
Mike

Against
Lisa
Katy
Amy

Conflict 3
Pete vs Minna: Pete wins

```{r}
file_id <- grepl("thuroff", files)

emma_vs_ann <- thurman_office_function("ANN", "EMMA")
emma_vs_group <- thurman_office_function("EMMA", c("ANN", "AMY", "TINA", "KATY","LISA"))
pete_vs_minna <-  thurman_office_function("PETE", "MINNA", remove_minna = FALSE)


test <- emma_vs_group$groups

bind_rows(#emma_vs_group$summary %>% mutate(model = "emma vs group"),
          emma_vs_ann$summary %>% mutate(model = "ann vs emma"),
          pete_vs_minna$summary %>%mutate(model = "pete vs minna")
            
            ) %>%
  mutate(name = str_remove(name, "clustering_" )%>% 
           str_replace(., "_", " ") %>% 
           str_replace(., "elev", "SETSe")) %>%
  ggplot(aes(x = ratio, y = fract, colour = name, group = name)) + geom_line() +
  facet_wrap(~model) +
  labs(title = "Predicted control using SETSe and traditional clustering methods", 
       x ="Odds ratio of business to personal weights",
       y = " fraction of nodes controlled") +
    theme(axis.text.x = element_text(angle = 55, hjust = 1))
ggsave(file.path(FiguresFolder,  "thurman_factional_control.pdf"))       

emma_vs_group$groups %>%
ggplot(aes(y = elevation, x = node, colour = elevation>0)) + geom_point()

emma_vs_ann$groups %>%
ggplot(aes(y = elevation, x = node)) + geom_point() +
    theme(axis.text.x = element_text(angle = 25, hjust = 1))


emma_vs_group$groups %>%
  filter(node=="PRESIDENT")

pete_vs_minna$g_out %>%
  delete.vertices(., "MINNA") %>%
ggraph(.) + 
    geom_edge_link2( width = 0.7, edge_alpha =0.5) + 
      geom_node_point( aes(
                           size = ifelse(name == "PETE"| name =="MINNA", 6,3))) + 
    scale_size_continuous(range = c(3, 6))+
  scale_edge_colour_viridis() +
  guides( size = "none")+
geom_node_text(aes(label = name), nudge_y = .08)

```

##Zachery Karate club

```{r}

```


##Sampson data
```{r}
g_dl <- load_dl_graph(files[7], directed = FALSE)


plot(g_dl[[3]])

names(g_dl)

```



#highschool

This is to see if using the highschool data I can generate more distinct results relating to spring strength as the networks are actual social networks as opposed to random structures.

```{r}

set.seed(123)
g <- read_rds(file.path(PLwd, "highschool/graphs", "school_7.rds" ))  %>% simplify() %>% {
  set_edge_attr(., "k", value = 500) } %>%
  remove_small_components()


ggraph(g) +
      geom_edge_fan()+
      geom_node_point(aes(colour = grade), size=3) 


g_df <- as_data_frame(g, what = "edges")

g <- g %>% 
two_beligerent_conflict(., beligerents = c(19, 23)) %>%
  prepare_SETSe_continuous(. , node_names = "name", force_var = "force")

results <- SETSe_auto(g)
results <- SETSe_bicomp(g, tol = 0.002, verbose = T)

sum(results$node_embeddings$elevation>0)
sum(results$node_embeddings$elevation<0)

test <- as_data_frame(g)
vcount(g)
```


	#Update packages

```{r}
library(devtools)
library(roxygen2)
```

rsetse update
```{r}
roxygenise( "~/rSETSe")
detach("package:rsetse", unload = TRUE)
install("~/rSETSe")
library(rsetse)
```

ConflcitInternal update
```{r}
roxygenise( "~/SETSe_conflict/ConflictInternal")
detach("package:ConflictInternal", unload = TRUE)
install("~/SETSe_conflict/ConflictInternal")
library(ConflictInternal)
```

	